---
title: "PA1_template.Rmd"
author: "Dean Woodley"
date: "Monday, December 26, 2016"
output: html_document
---
Loading and preprocessing the data
Show any code that is needed to Load the data

1.  Process/transform the data (if necessary) into a format suitable for your analysis
```{r}
## Add code here

```


2.  What is mean total number of steps taken per day?
    For this part of the assignment, you can ignore the missing values in the dataset.
```{r}
## Add code here

```

3.  Calculate the total number of steps taken per day.
```{r}
## Add code here

```

4.  Calculate and report the mean and median of the total number of steps taken per day.
```{r}
## Add code here

```


5.  What is the average daily activity pattern?
    Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) 
    and the average number of steps taken, averaged across all days (y-axis)
```{r, echo=TRUE}
## Add code here

```
   
   
6.  Which 5-minute interval, on average across all the days in the dataset, 
    contains the maximum number of steps?
```{r}
## Add code here

```

7.  Calculate and report the total number of missing values in the dataset 
    (i.e. the total number of rows with NAs)
```{r}
## Add code here

```
   

8.  Devise a strategy for filling in all of the missing values in the dataset. 
    The strategy does not need to be sophisticated. For example, you could use 
    the mean/median for that day, or the mean for that 5-minute interval, etc.
```{r}
## Add code here

```



9.  Create a new dataset that is equal to the original dataset but with the 
    missing data filled in.
    
    Make a histogram of the total number of steps taken each day and calculate 
    and report the mean and median total number of steps taken per day. Do these 
    values differ from the estimates from the first part of the assignment? 
    What is the impact of imputing missing data on the estimates of the total 
    daily number of steps?
```{r, echo=TRUE}
## Add code here

```
   
   
10. Are there differences in activity patterns between weekdays and weekends?
    For this part the weekdays() function may be of some help here. Use the 
    dataset with the filled-in missing values for this part. Create a new factor 
    variable in the dataset with two levels - "weekday" and "weekend" 
    indicating whether a given date is a weekday or weekend day.
```{r}
## Add code here

```

11. Make a panel plot containing a time series plot (i.e. type = "l") of the 
    5-minute interval (x-axis) and the average number of steps taken, averaged 
    across all weekday days or weekend days (y-axis). See the README file in 
    the GitHub repository to see an example of what this plot should look like 
    using simulated data.
```{r, echo=TRUE}
## Add code here

```
